Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Small revisions to Methodology

Our survey contained two main sections.
In one section, we presented participants with scenarios---something undesirable a wearable device might do---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity of the impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior risk perception studies, as we describe next.

%Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies. To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to relatively rank several technologies by both their risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.

>>>>

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity of the impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior risk perception studies, as we describe next.

%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of the following 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies and how those perceptions compared to other well-established technologies. To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.
